Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-28 doc/prelim/presentation/prelim_presentation.tex
added mc preliminaries

%%---------------------------------------------------------------------------%%
\begin{frame}{Parallel Projection Method Notes}

\begin{itemize}
  \item Global reduction operations observed not to impede scalability
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
      \item Matrix-vector multiply
      \item Weak scaling is better
    \end{itemize}
\end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Monte Carlo Solution Methods for Linear Problems}

@@

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Projection Method Notes}

\begin{itemize}
  \item Global reduction operations observed not to impede scalability
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
      \item Matrix-vector multiply
      \item Weak scaling is better
    \end{itemize}

\end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Monte Carlo Solution Methods for Discrete Linear Systems}

  \begin{itemize}
    \item First proposed by J. Von Neumann and S.M. Ulam in the 1940's
    \item Earliest published reference in 1950
    \item General lack of published work
    \item Modern work by Evans and others has yielded new applications
    \item No indication of parallel methods in the literature
  \end{itemize}
\end{frame}

  \begin{itemize}
  \item Split the operator
  \end{itemize}

  \[
  \ve{H} = \ve{I} - \ve{A}
  \]

  \[
  \ve{x} = \ve{H} \ve{x} + \ve{b}
  \]

  \begin{itemize}
  \item Generate the \textit{Neumann series}
  \end{itemize}

  \[
  \ve{A}^{-1} = (\ve{I}-\ve{H})^{-1} = \sum_{k=0}^{\infty} \ve{H}^k
  \]

  \begin{itemize}
  \item Require $\rho(\ve{H}) < 1$ for convergence
  \end{itemize}

  \[
  \ve{A}^{-1}\ve{b} = \sum_{k=0}^{\infty} \ve{H}^k\ve{b} = \ve{x}
  \]

@@

  \begin{itemize}
  \item Expand the Nuemann series
  \end{itemize}

  \[
  x_i = \sum_{k=0}^{\infty}\sum_{i_1}^{N}\sum_{i_2}^{N}\ldots
  \sum_{i_k}^{N}h_{i,i_1}h_{i_1,i_2}\ldots h_{i_{k-1},i_k}b_{i_k}
  \]

  \begin{itemize}
  \item Define a sequence of state transitions
  \end{itemize}

  \[
  \nu = i \rightarrow i_1 \rightarrow \cdots \rightarrow i_{k-1}
  \rightarrow i_{k}
  \]

  \begin{itemize}
  \item Define the \textit{Neumann-Ulam decomposition}\footnote{The
    Hadamard product $\ve{A} = \ve{B} \circ \ve{C}$ is defined
    element-wise as $a_{ij} = b_{ij} c_{ij}$.}
  \end{itemize}

  \[
  \ve{H} = \ve{P} \circ \ve{W}
  \]
